|

### 2021-09-22 article/articleCustomerDropoutMembership.Rmd
upd

c_index = concordance_index(csf, X_test, t_test, e_test)
ibs = integrated_brier_score(csf, X_test, t_test, e_test, t_max=12, figure_size=(12,5))
results = compare_to_actual(csf, X_test, t_test, e_test, is_at_risk = False,  figure_size=(12, 6), metrics = ['rmse', 'mean', 'median'])
```

@@

    # Fitting the model
    csf = RandomSurvivalForestModel(num_trees=200)
    csf.fit(X_train, T_train, E_train, max_features='sqrt', max_depth=5, min_node_size=20)
```

>>>>

c_index = concordance_index(csf, X_test, t_test, e_test)
ibs = integrated_brier_score(csf, X_test, t_test, e_test, t_max=12, figure_size=(12,5))
results = compare_to_actual(csf, X_test, t_test, e_test, is_at_risk = False,  figure_size=(12, 6), metrics = ['rmse', 'mean', 'median'])

print(results)
```

@@

    # Fitting the model
    csf = RandomSurvivalForestModel(num_trees=200)
    csf.fit(X_train, T_train, E_train, max_features='sqrt', max_depth=5, min_node_size=20)
    c_index = concordance_index(csf, X_test, t_test, e_test)
    ibs = integrated_brier_score(csf, X_test, t_test, e_test, t_max=12, figure_size=(12,5))
    results_clusters = compare_to_actual(csf, X_test, t_test, e_test, is_at_risk = False,  figure_size=(12, 6), 
                                metrics = ['rmse', 'mean', 'median'])
    print(results_clusters)
```
